Argennon: A Scalable Smart Contract Platform

### 2021-07-19 tex/sections/consensus.tex
Fix a readability issue
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

As we mentioned before, the block with height $n$ needs a certificate from the committee of
validators with index $n$ modulo $m$. To decide about signing a block certificate, a validator
checks the conditional validity\footnote{See Section~\ref{subsec:block-validation}} of the block, and
if the block is valid he issues
an "accept" signature. If the block is invalid, he initiates the recovery protocol. The validator will broadcast the
certificate \textbf{only after} he sees the certificate of the validators of the previous block.
Some validators may also require seeing a certificate from
some community driven committee. An honest validator never signs a certificate for two different blocks with the
same height.

>>>>

As we mentioned before, the block with height $n$ needs a certificate from the committee of
validators with index $n$ modulo $m$. To decide about signing the certificate of a block which already has
a certificate from the delegates, a validator checks the conditional
validity\footnote{See Section~\ref{subsec:block-validation}} of the block, and
if the block is valid he issues
an "accept" signature. If the block is invalid, he initiates the recovery protocol. The validator will broadcast the
certificate \textbf{only after} he sees the certificate of the validators of the previous block.
Some validators may also require seeing a certificate from
some community driven committee. An honest validator never signs a certificate for two different blocks with the
same height.
